---
title: "R Notebook"
output: html_notebook
---

Forecasting Australian Wine Sales: Figure 6.15 shows time plots of monthly sales of six types of Australian wines (red, rose, sweet white, dry white, sparkling, and fortified) for 1980-1994. Data available in AustralianWines.xls. 10 The units are thousands of 10 Source: R. J. Hyndman Time Series Data Library, http://data.is/TSDLdemo; accessed on Mar 28, 2016 liters. You are hired to obtain short-term forecasts (2-3 months ahead) for each of the six series, and this task will be repeated every month. 

```{r}
library(forecast)
```


```{r, message=FALSE, warning=FALSE}
wine <- read.csv("AustralianWines.csv", header = T)
head(wine)

```

```{r}
#read in each as a time series and partition
#fortified
Fortified.ts <- ts(wine$Fortified, start = c(1980, 1), frequency = 12)
FortifiedvalidLength <- 12
FortifiedtrainLength <- length(Fortified.ts) - FortifiedvalidLength
FortifiedsalesTrain <- window(Fortified.ts, end = c(1980, FortifiedtrainLength))
FortifiedsalesValid <- window(Fortified.ts, start = c(1980, FortifiedtrainLength + 1))
#Red
Red.ts <- ts(wine$Red, start = c(1980, 1), frequency = 12)
RedvalidLength <- 12
RedtrainLength <- length(Red.ts) - RedvalidLength
RedsalesTrain <- window(Red.ts, end = c(1980, RedtrainLength))
RedsalesValid <- window(Red.ts, start = c(1980, RedtrainLength + 1))
#Rose
Rose.ts <- ts(wine$Rose, start = c(1980, 1), frequency = 12)
RosevalidLength <- 12
RosetrainLength <- length(Rose.ts) - RosevalidLength
RosesalesTrain <- window(Rose.ts, end = c(1980, RosetrainLength))
RosesalesValid <- window(Rose.ts, start = c(1980, RosetrainLength + 1))
#parkling
Sparkling.ts <- ts(wine$sparkling, start = c(1980, 1), frequency = 12)
SparklingvalidLength <- 12
SparklingtrainLength <- length(Sparkling.ts) - SparklingvalidLength
SparklingsalesTrain <- window(Sparkling.ts, end = c(1980, SparklingtrainLength))
SparklingsalesValid <- window(Sparkling.ts, start = c(1980, SparklingtrainLength + 1))
#Sweet
Sweet.white.ts <- ts(wine$Sweet.white, start = c(1980, 1), frequency = 12)
SweetvalidLength <- 12
SweettrainLength <- length(Sweet.white.ts) - SweetvalidLength
SweetsalesTrain <- window(Sweet.white.ts, end = c(1980, SweettrainLength))
SweetsalesValid <- window(Sweet.white.ts, start = c(1980, SweettrainLength + 1))
#Dry
Dry.white.ts <- ts(wine$Dry.white, start = c(1980, 1), frequency = 12)
DryvalidLength <- 12
DrytrainLength <- length(Dry.white.ts) - DryvalidLength
DrysalesTrain <- window(Dry.white.ts, end = c(1980, DrytrainLength))
DrysalesValid <- window(Dry.white.ts, start = c(1980, DrytrainLength + 1))

#plots
par(mfrow = c(2,3))
plot(Fortified.ts, xlab = "Year", ylab = "Sales (thousands)", col = "deeppink4", main = "Fortified Wine Sales")
plot(Red.ts, xlab = "Year", ylab = "Sales (thousands)", col = "deeppink4", main = "Red Wine Sales")
plot(Rose.ts, xlab = "Year", ylab = "Sales (thousands)", col = "deeppink4", main = "Rose Sales")
plot(Sparkling.ts, xlab = "Year", ylab = "Sales (thousands)", col = "deeppink4", main = "Sparkling Sales")
plot(Sweet.white.ts, xlab = "Year", ylab = "Sales (thousands)", col = "deeppink4", main = "Sweet Wine Sales")
plot(Dry.white.ts, xlab = "Year", ylab = "Sales (thousands)", col = "deeppink4", main = "Dry Wine Sales")



























```

1. Would you consider neural networks for this task? Explain why. 

2. Use neural networks to forecast fortified wine sales, as follows: 

* Partition the data using the period until December 1993 as the training period.

* Run a neural network using R’s nnetar with 11 nonseasonal lags (i.e., p = 11). Leave all other arguments at their default. 

  (a) Create a time plot for the actual and forecasted series over the training period. Create also a time plot of the forecast errors for the training period. Interpret what you see in the plots. 
  
  (b) Use the neural network to forecast sales for each month in the validation period (January 1994 to December 1994). 
  
3. Compare your neural network to an exponential smoothing model used to forecast fortified wine sales. 

  (a) Use R’s ets function to automatically select and fit an exponential smoothing model to the training period until December 1993. Which model did ets fit?
  
  (b) Use this exponential smoothing model to forecast sales for each month in 1994. 
  
  (c) How does the neural network compare to the exponential smoothing model in terms of predictive performance in the training period? In the validation period?



