---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
  word_document: default
---

Sigco, Inc is a glass and architectural metal fabricator/distributor in Westbrook, ME and serves much New England. They manufacture a number of glass products and think the demand for these products is seasonal. 

Inventory management is a major challenge. It is predominantly manual - inventory is counted three times a week to ensure accuracy, demand is forecasted just one week in advance and quantities to order for replenishment (including safety stock levels) are very subjective.  In particular, safety stock is computed by assigning an extra percentage of product to keep on hand of some of the products, but not all, and the percentage used varies by product. There is opportunity for analysis and improvement in the forecasting of demand using historical seasonal data.  Further, safety stock could be calculated to ensure greater efficiency of their inventory - maintaining or improving their service level while minimizing too much stock on hand.

The **goal** of this project is to build a systematic forecasting model evaluation tool for the company to use in its calculations for safety stock and reorder points using the EOQ model. An interactive forecasting tool, such as an R Shiny app, provides a simple means for management to upload data sets, visualize the historical use of products in graphical form, determine components inherent in the data, partition the data into training and validation sets, run a few different fit models , evaluate the performance of the models, choose the best model to deploy a forecast, and use that forecast in the calculation of the safety stock and reorder points. 

**Everything we do in the class relies on data, where and how do you expect to obtain the necessary time series data to utilize the tools and models we covered in class?** 

The data is easy to come by. The historical use of each item is documented on annual Excel spreadsheets that the company keeps. There are roughly 200 SKUs in Sigco's inventory, and I have choen to look at the 25 most utilized items and forecast their use. 

**Step 1**

Visualization

Import the company spreadsheets into R, clean them up, and combine them into a single time series data set starting from January, 2012. Not all items have been in the company's inventory since then, but the majority have. 


```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(dplyr)
library(tidyr)
library(forecast)
library(pander)
library(reshape2)
library(zoo)
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
Stock12 <- read.csv("Inventory12.csv", header = T, stringsAsFactors = F)
Stock12 <- Stock12 %>% select(-Description)
names(Stock12) <- c("Item_Code", "01-12", "02-12", "03-12", "04-12", "05-12", "06-12", "07-12", "08-12", "09-12", "10-12", "11-12", "12-12")
Stock12 <- gather(Stock12, Month, Used,c(2:13))
ItemstoUse <-  c("SS06CLR96130","SS03CLR96130" , "SS12CLR102130", "SS02CLR7284", "SS06S6T100144", "SS10CLR96130", "SS05CLR96130", "SS06MCL96130", "SS06S6A100144" , "SS10SHG96130", "SS03LOE7284", "SS03LOE728", "SS03S6T7284", "SS04CLR96130", "SS06LOE96130", "SS02LOE7284", "SS06S7T100144", "SS05S6T96130", "SS06BRN96130","SS06GRY96130","SS06STP96130","SS03S6A7284","SS10SUW96130","SS0LCLR7284","SS05LOE96130","SS12SHG96130","SS06STC102144","SS12STP96130","SS06S6G96130","SS10STP96130")
Stock12 <- Stock12 %>% filter(Item_Code %in% ItemstoUse)
#pander(head(Stock12))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Stock13 <- read.csv("Inventory13.csv", header = T, stringsAsFactors = F)
Stock13 <- Stock13 %>% select(-Description)
names(Stock13) <- c("Item_Code", "01-13", "02-13", "03-13", "04-13", "05-13", "06-13", "07-13", "08-13", "09-13", "10-13", "11-13", "12-13")
Stock13 <- gather(Stock13, Month, Used,c(2:13))
Stock13 <- Stock13 %>% filter(Item_Code %in% ItemstoUse)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#wide to long 2014
Stock14 <- read.csv("Inventory14.csv", header = T, stringsAsFactors = F)
Stock14 <- Stock14 %>% select(-Description)
names(Stock14) <- c("Item_Code", "01-14", "02-14", "03-14", "04-14", "05-14", "06-14", "07-14", "08-14", "09-14", "10-14", "11-14", "12-14")
Stock14 <- gather(Stock14, Month, Used,c(2:13))
Stock14 <- Stock14 %>% filter(Item_Code %in% ItemstoUse)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#wide to long 2015
Stock15 <- read.csv("Inventory15.csv", header = T, stringsAsFactors = F)
Stock15 <- Stock15[-1,]
Stock15 <- Stock15 %>% select(-Description)
names(Stock15) <- c("Item_Code", "01-15", "02-15", "03-15", "04-15", "05-15", "06-15", "07-15", "08-15", "09-15", "10-15", "11-15", "12-15")
Stock15 <- gather(Stock15, Month, Used,c(2:13))
Stock15 <- Stock15 %>% filter(Item_Code %in% ItemstoUse)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Stock16 <- read.csv("Inventory16.csv", header = T, stringsAsFactors = F)
Stock16 <- Stock16[-1,]
Stock16 <- Stock16 %>% select(-Description)
names(Stock16) <- c("Item_Code", "01-16", "02-16", "03-16", "04-16", "05-16", "06-16", "07-16", "08-16", "09-16", "10-16", "11-16", "12-16")
Stock16 <- gather(Stock16, Month, Used,c(2:13))
Stock16 <- Stock16 %>% filter(Item_Code %in% ItemstoUse)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Stock17 <- read.csv("Inventory17.csv", header = T, stringsAsFactors = F)
Stock17 <- Stock17 %>% select(-Description)
names(Stock17) <- c("Item_Code", "01-17", "02-17", "03-17", "04-17")
Stock17 <- gather(Stock17, Month, Used,c(2:5))
Stock17 <- Stock17 %>% filter(Item_Code %in% ItemstoUse)
```

The final data set will look something like this: 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
x <- rbind.data.frame(Stock12, Stock13, Stock14, Stock15, Stock16, Stock17)
x[x == 0] <- NA
kable(head(x, 20))
```

**Step 2**

Visualize the data. I have chosen 2 different Items. 

```{r, message=FALSE, warning=FALSE, include=FALSE}
a <- x %>% filter(Item_Code == "SS06CLR96130")
a$Used <- as.numeric(a$Used)
a.ts <- ts(a$Used, start = c(2012,1), frequency = 12)
ggseasonplot(a.ts)
```

```{r, echo=FALSE, warning=FALSE}
validLength <- 4
trainLength <- length(a.ts) - validLength
salesTrain <- window(a.ts, end = c(2012, trainLength))
salesValid <- window(a.ts, start = c(2012, trainLength + 1))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
b <- x %>% filter(Item_Code == "SS02LOE7284")
b$Used <- as.numeric(b$Used)
b.ts <- ts(b$Used, start = c(2012,1), frequency = 12)

```


```{r, message=FALSE, warning=FALSE, include=FALSE}
#out of use
c <- x %>% filter(Item_Code == "SS03CLR96130")
c$Used <- as.numeric(c$Used)
c.ts <- ts(c$Used, start = c(2012,1), frequency = 12)

```

```{r clearly seasonal, message=FALSE, warning=FALSE, include=FALSE}
d <- x %>% filter(Item_Code == "SS02CLR7284")
d$Used <- as.numeric(d$Used)
d.ts <- ts(d$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
e <- x %>% filter(Item_Code == "SS06S6T100144")
e$Used <- as.numeric(e$Used)
e.ts <- ts(e$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
f <- x %>% filter(Item_Code == "SS10CLR96130")
f$Used <- as.numeric(f$Used)
f.ts <- ts(f$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
g <- x %>% filter(Item_Code == "SS05CLR96130")
g$Used <- as.numeric(g$Used)
g.ts <- ts(g$Used, start = c(2012,1), frequency = 12)

```

```{r}
h <- x %>% filter(Item_Code == "SS06MCL96130")
h$Used <- as.numeric(h$Used)
h.ts <- ts(h$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
i <- x %>% filter(Item_Code == "SS06S6A100144")
i$Used <- as.numeric(i$Used)
i.ts <- ts(i$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
j <- x %>% filter(Item_Code == "SS10SHG96130")
j$Used <- as.numeric(j$Used)
j.ts <- ts(j$Used, start = c(2012,1), frequency = 12)

```



```{r, message=FALSE, warning=FALSE, include=FALSE}
k <- x %>% filter(Item_Code == "SS12CLR102130")
k$Used <- as.numeric(k$Used)
k.ts <- ts(k$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
l <- x %>% filter(Item_Code == "SS03LOE7284")
l$Used <- as.numeric(l$Used)
l.ts <- ts(l$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
m <- x %>% filter(Item_Code == "SS03S6T7284")
m$Used <- as.numeric(m$Used)
m.ts <- ts(m$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
n <- x %>% filter(Item_Code == "SS04CLR96130")
n$Used <- as.numeric(n$Used)
n.ts <- ts(n$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}

o <- x %>% filter(Item_Code == "SS06LOE96130")
o$Used <- as.numeric(o$Used)
o.ts <- ts(o$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
p <- x %>% filter(Item_Code == "SS02LOE7284")
p$Used <- as.numeric(p$Used)
p.ts <- ts(p$Used, start = c(2012,1), frequency = 12)


```

```{r, message=FALSE, warning=FALSE, include=FALSE}
q <- x %>% filter(Item_Code == "SS06S7T100144")
q$Used <- as.numeric(q$Used)
q.ts <- ts(q$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
r <- x %>% filter(Item_Code == "SS05S6T96130")
r$Used <- as.numeric(r$Used)
r.ts <- ts(r$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
s <- x %>% filter(Item_Code == "SS06BRN96130")
s$Used <- as.numeric(s$Used)
s.ts <- ts(s$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
t <- x %>% filter(Item_Code == "SS06GRY96130")
t$Used <- as.numeric(t$Used)
t.ts <- ts(t$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
u <- x %>% filter(Item_Code == "SS06STP96130")
u$Used <- as.numeric(u$Used)
u.ts <- ts(u$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
v <- x %>% filter(Item_Code == "SS03S6A7284")
v$Used <- as.numeric(v$Used)
v.ts <- ts(v$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
w <- x %>% filter(Item_Code == "SS10SUW96130")
w$Used <- as.numeric(w$Used)
w.ts <- ts(w$Used, start = c(2012,1), frequency = 12)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
xx <- x %>% filter(Item_Code == "SS0LCLR7284")
xx$Used <- as.numeric(xx$Used)
xx.ts <- ts(xx$Used, start = c(2012,1), frequency = 12)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
y <- x %>% filter(Item_Code == "SS05LOE96130")
y$Used <- as.numeric(y$Used)
y.ts <- ts(y$Used, start = c(2013,10), frequency = 12)


```


```{r, message=FALSE, warning=FALSE, include=FALSE}
z <- x %>% filter(Item_Code == "SS12SHG96130")
z$Used <- as.numeric(z$Used)
z.ts <- ts(z$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
aa <- x %>% filter(Item_Code == "SS06STC102144")
aa$Used <- as.numeric(aa$Used)
aa.ts <- ts(aa$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
bb <- x %>% filter(Item_Code == "SS12STP96130")
bb$Used <- as.numeric(bb$Used)
bb.ts <- ts(bb$Used, start = c(2012,1), frequency = 12)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
cc <- x %>% filter(Item_Code == "SS06S6G96130")
cc$Used <- as.numeric(cc$Used)
cc.ts <- ts(cc$Used, start = c(2012,1), frequency = 12)

```


```{r, message=FALSE, warning=FALSE, include=FALSE}
dd <- x %>% filter(Item_Code == "SS10STP96130")
dd$Used <- as.numeric(dd$Used)
dd.ts <- ts(dd$Used, start = c(2012,1), frequency = 12)


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
par(mfrow = c(2,3))
plot(a.ts)
plot(b.ts)
plot(d.ts)
plot(e.ts)
plot(f.ts)
plot(o.ts)

par(mfrow = c(2,3))
plot(m.ts)
plot(n.ts)
plot(g.ts)
plot(i.ts)
plot(j.ts)
plot(s.ts)

par(mfrow = c(2,3))
plot(t.ts)
plot(u.ts)
plot(p.ts)
plot(q.ts)
plot(r.ts)
plot(dd.ts)

par(mfrow = c(2,3))
plot(v.ts)
plot(w.ts)
plot(z.ts)
plot(bb.ts)
plot(l.ts)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#colors <- rainbow(6, start = .7, end = 0.9)
colors <- c("violetred", "turquoise3", "tomato", "skyblue2", "seagreen3","goldenrod1" )
#colors <- terrain.colors(6)

par(mfrow = c(2,3))
seasonplot(a.ts, col = colors)
seasonplot(b.ts, col = colors)
seasonplot(d.ts, col = colors)
seasonplot(e.ts, col = colors)
seasonplot(f.ts, col = colors)
seasonplot(o.ts, col = colors)

par(mfrow = c(2,3))

seasonplot(m.ts, col = colors)
seasonplot(n.ts, col = colors)
seasonplot(g.ts, col = colors)
seasonplot(i.ts, col = colors)
seasonplot(j.ts, col = colors)
seasonplot(s.ts, col = colors)

par(mfrow = c(2,3))

seasonplot(t.ts, col = colors)
seasonplot(u.ts, col = colors)
seasonplot(p.ts, col = colors)
seasonplot(q.ts, col = colors)
seasonplot(r.ts, col = colors)
seasonplot(dd.ts, col = colors)

par(mfrow = c(2,3))

seasonplot(v.ts, col = colors)
seasonplot(w.ts, col = colors)
seasonplot(z.ts, col = colors)
seasonplot(bb.ts, col = colors)
seasonplot(l.ts, col = colors)
```

For brevity's sake, I'll narrow the scope to 6 SKUs, e,f,m,n,o,s because, as a group, I can illustrate how the company can model data that exhibits differing components.

Trend

```{r, echo=FALSE, message=FALSE, warning=FALSE}
validLengthM <- 12
trainLengthM <- length(m.ts) - validLengthM
salesTrainM <- window(m.ts, end = c(2012, trainLengthM))
salesValidM <- window(m.ts, start = c(2012, trainLengthM + 1))
LinearM <- tslm(m.ts ~ trend)
polyLinearM <- tslm(m.ts ~ trend + I(trend^2))
seasonTrendM <- tslm(m.ts ~ trend + season)
summary(LinearM)

#naive
naiveM <- snaive(salesTrainM, h = validLengthM)
#pointFC
naiveM$mean
#accuracy 81/34
accuracy(naiveM, salesValidM)


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
validLengthN <- 12
trainLengthN <- length(n.ts) - validLengthN
salesTrainN <- window(n.ts, end = c(2012, trainLengthN))
salesValidN <- window(n.ts, start = c(2012, trainLengthN + 1))
LinearN <- tslm(n.ts ~ trend)
polyLinearN <- tslm(n.ts ~ trend + I(trend^2))
seasonTrendN <- tslm(n.ts ~ trend + season)
summary(LinearN)
#naive
naiveN <- snaive(salesTrainN, h = validLengthN)
#pointFC
naiveN$mean
#accuracy 17/13
accuracy(naiveN, salesValidN)

```

```{r, partition}
validLengthS <- 12
trainLengthS <- length(s.ts) - validLengthS
salesTrainS <- window(s.ts, end = c(2012, trainLengthS))
salesValidS <- window(s.ts, start = c(2012, trainLengthS + 1))
```

```{r, trend and seasonality}
LinearS <- tslm(s.ts ~ trend)
polyLinearS <- tslm(s.ts ~ trend + I(trend^2))
seasonTrendS <- tslm(s.ts ~ trend + season)
summary(seasonTrendS)
```

```{r, Acf Trend and Seasonality}
#Autocorrelation
AcfS <- Acf(s.ts)
AcfS
#Acf for Differenced and there appears to be some uncaptured seasonality
Acf(diff(s.ts, lag = 1), lag.max = 12, main = "Acf Plot for Differenced Item S")
plot(diff(s.ts, lag = 1, bty = "l", main = "Uncaptured Seasonality in Differenced \nItem S Monthly Data"))
abline(h = 0)
#test for a random walk
fitS <- Arima(s.ts, order = c(1,0,0))
fitS
2*pt(-abs((1-fitS$coef["ar1"]) / 0.1239), df = length(s.ts)-1)
#normal distribution
2*pnorm(-abs((1 - fitS$coef["ar1"]) / 0.1239))
```

Since $p<\alpha$ we know this series is not a random walk

```{r, forecast regression}
seasonTrendS <- tslm(salesTrainS ~ trend + season)
#summary
summary(seasonTrendS)
#forecasting Regression Models
seasonRegSForecast <- forecast(seasonTrendS, h = validLengthS)
seasonRegSForecast
#accuracy 30/25
accuracy(seasonRegSForecast, salesValidS)
```

**Shows not much left to model**

```{r}
residualsseasonTrendS <- Acf(seasonTrendS$residuals)
```

**If more to model, follow this process**

```{r}
ARModel <- Arima(seasonTrendS$residuals, order = c(1,0,0))
ARModel
#calculate t stat, see it's not statistically significant
ARModel$coef["ar1"] / 0.1359
#residuals of residuals
Acf(ARModel$residuals)
#forecast residuals
errorForecast <- forecast(ARModel, h = validLengthS)
errorForecast
#improved Forecast MAPE = 25.27023
adjustedForecast <- seasonRegSForecast$mean + errorForecast$mean
adjustedForecast
accuracy(adjustedForecast, salesValidS)
```


```{r}
#naive
naiveS <- snaive(salesTrainS, h = validLengthS)
#pointFC
naiveS$mean
#accuracy 43/21
accuracy(naiveS, salesValidS)
```

```{r}
#trailing
trailMAS <- rollmean(salesTrainS, k = 12, align = "right")
trailSForecast <- trailMAS[1]
trailSForecast
accuracy(trailSForecast, salesValidS[1])
#look for trend and seasonality with Acf
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#best smoothing model, it chooses an ANN model with a very small alpha meaning it's a slow learner.
etsS <- ets(salesTrainS, model = "ZZZ")
etsS
summary(etsS)
etsForecastS <- forecast(etsS, h = validLengthS, level = 0)
etsForecastS
#accuracy 42/24
accuracy(etsForecastS, salesValidS)
plot(s.ts, main = "Smoothing Model S", bty = "l")
lines(etsS$fitted, col = "blue", lty = 1,lwd = 2)
lines(etsSANN$fitted, col = "green", lty = 1,lwd = 2)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
validLengthE <- 12
trainLengthE <- length(e.ts) - validLengthE
salesTrainE <- window(e.ts, end = c(2012, trainLengthE))
salesValidE <- window(e.ts, start = c(2012, trainLengthE + 1))
LinearE <- tslm(e.ts ~ trend)
polyLinearE <- tslm(e.ts ~ trend + I(trend^2))
#seasonality does not show much significance
seasonTrendE <- tslm(e.ts ~ trend + season)
summary(LinearE)
#naive
naiveE <- snaive(salesTrainE, h = validLengthE)
#pointFC snaive 42/28 naive 29/14
naiveE$mean
#accuracy 43/21
accuracy(naiveE, salesValidE)

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
validLengthF <- 12
trainLengthF <- length(f.ts) - validLengthF
salesTrainF <- window(f.ts, end = c(2012, trainLengthF))
salesValidF <- window(f.ts, start = c(2012, trainLengthF + 1))
LinearF <- tslm(f.ts ~ trend)
polyLinearF <- tslm(f.ts ~ trend + I(trend^2))
seasonTrendF <- tslm(f.ts ~ trend + season)
summary(LinearF)
#naive
naiveF <- snaive(salesTrainF, h = validLengthF)
#pointFC snaive 22/13 naive 20/14
naiveF$mean
#accuracy 43/21
accuracy(naiveF, salesValidF)

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
validLengthO <- 12
trainLengthO <- length(o.ts) - validLengthO
salesTrainO <- window(o.ts, end = c(2012, trainLengthO))
salesValidO <- window(o.ts, start = c(2012, trainLengthO + 1))
LinearO <- tslm(o.ts ~ trend)
polyLinearO <- tslm(o.ts ~ trend + I(trend^2))
seasonTrendO <- tslm(o.ts ~ trend + season)
summary(LinearO)
#naive
naiveO <- snaive(salesTrainO, h = validLengthO)
#pointFC snaive 85/40 naive 115/36
naiveO$mean
#accuracy 43/21
accuracy(naiveO, salesValidO)
```

Naive Forecasting

**Item E Naive**

```{r, echo=FALSE, message=FALSE, warning=FALSE}
pander(accuracy(naiveE, salesValidE))
```

**Item F Naive**

```{r, echo=FALSE, message=FALSE, warning=FALSE}
pander(accuracy(naiveF, salesValidF))
```

**Item M Naive**

```{r}
pander(accuracy(naiveM, salesValidM))
```

**Item N Naive**

```{r, echo=FALSE, message=FALSE, warning=FALSE}
pander(accuracy(naiveN, salesValidN))
```

**Item O Naive**

```{r, echo=FALSE, message=FALSE, warning=FALSE}
pander(accuracy(naiveO, salesValidO))
```

**Item S Naive**

```{r, echo=FALSE, message=FALSE, warning=FALSE}
pander(accuracy(naiveS, salesValidS))
```



```{r, echo=FALSE, message=FALSE, warning=FALSE}
par(mfrow = c(1,2))

plot(e.ts, main = "Monthly Use Item E \nTrend and Seasonality", bty = "l")
lines(LinearF$fitted, col = "blue", lwd = 2)
lines(polyLinearE$fitted, col = "green", lwd = 2)
lines(seasonTrendE$fitted, col = "orange", lwd = 2)
legend(2012, 800, c("L R-sq = .77 ", "Q R-sq = .76", "S Rs-sq = .77"), lty = c(1,1,1), lwd = c(2,2,2), col = c("blue", "green", "orange"), bty = "n" )

plot(f.ts, main = "Monthly Use Item F \nTrend and Seasonality", bty = "l")
lines(LinearF$fitted, col = "blue", lwd = 2)
lines(polyLinearF$fitted, col = "green", lwd = 2)
lines(seasonTrendF$fitted, col = "orange", lwd = 2)
legend(2012, 600, c("L R-sq = .61", "Q R-sq = 62", "S R-sq = .67"), lty = c(1,1,1), lwd = c(2,2,2), col = c("blue", "green", "orange"), bty = "n" )

par(mfrow = c(1,2))
plot(m.ts, main = "Monthly Use Item M \nTrend and Seasonality", bty = "l")
lines(LinearM$fitted, col = "blue", lwd = 2)
lines(polyLinearM$fitted, col = "green", lwd = 2)
lines(seasonTrendM$fitted, col = "orange", lwd = 2)
legend(2012, 250, c("L R-sq = .73", "Q R-sq = .79", "S R-sq = .74"), lty = c(1,1,1), lwd = c(2,2,2), col = c("blue", "green", "orange"), bty = "n" )

plot(n.ts, main = "Monthly Use Item N \nTrend and Seasonality", bty = "l", xlim = c(2012,2018))
lines(LinearN$fitted, col = "blue", lwd = 2)
lines(polyLinearN$fitted, col = "green", lwd = 2)
lines(seasonTrendN$fitted, col = "orange", lwd = 2)
legend(2012, 380, c("L - none", "Q - none", "S R-sq = .78"), lty = c(1,1,1), lwd = c(2,2,2), col = c("blue", "green", "orange"), bty = "n" )

par(mfrow = c(1,2))
plot(o.ts,main = "Monthly Use Item O \nTrend and Seasonality", bty = "l")
lines(LinearO$fitted, col = "blue", lwd = 2)
lines(polyLinearO$fitted, col = "green", lwd = 2)
lines(seasonTrendO$fitted, col = "orange", lwd = 2)
legend(2012, 350, c("L R-sq = .52", "Q R-sq = .62", "S R-sq = .52"), 
       lty = c(1,1,1), lwd = c(2,2,2), 
       col = c("blue", "green", "orange"), bty = "n" )

plot(s.ts, main = "Monthly Use Item S \nTrend and Seasonality", bty = "l")
lines(LinearS$fitted, col = "blue", lty = 1,lwd = 2)
lines(polyLinearS$fitted, col = "green", lty = 1,lwd = 2)
lines(seasonTrendS$fitted, col = "orange", lty = 1,lwd = 2)
legend(2012, 200, c("L - none", "Q - none", "S R-sq = 0.2"), 
       lty = c(1,1,1), lwd = c(2,2,2), 
       col = c("blue", "green", "orange"), bty = "n" )


```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
par(mfrow = c(1,2))
xrange <- c(1,7)
yrange <- c(0,1000)

plot(xrange, yrange, type = "n", xlab = "Year", ylab = "Inventory Used", bty = "l")
colors <- rainbow(12)
linetype <- 1

for(i in 1:12){

  currentMonth <- subset(e.ts, cycle(e.ts) == i)
  lines(currentMonth, type = "l", lwd = 1,
       
  col =colors[i]
 
  )
}
title("Item E - Inventory Used \nBroken out by Month ")

xrange <- c(1,7)
yrange <- c(100,600)

plot(xrange, yrange, type = "n", xlab = "Year", ylab = "Inventory Used", bty = "l")
colors <- rainbow(12)
linetype <- 1

for(i in 1:12){

  currentMonth <- subset(f.ts, cycle(f.ts) == i)
  lines(currentMonth, type = "l", lwd = 1,
       
  col =colors[i]
 
  )
}
title("Item F - Inventory Used \nBroken out by Month ")

legend(6.5,600, 1:12, cex = 0.8, col = colors,lty = linetype, title = "Month", xpd = NA, bty = "n")

par(mfrow = c(1,2))
xrange <- c(1,7)
yrange <- c(0,250)

plot(xrange, yrange, type = "n", xlab = "Year", ylab = "Inventory Used", bty = "l")
colors <- rainbow(12)
linetype <- 1

for(i in 1:12){

  currentMonth <- subset(m.ts, cycle(m.ts) == i)
  lines(currentMonth, type = "l", lwd = 1,
       
  col =colors[i]
 
  )
}
title("Item M - Inventory Used \nBroken out by Month ")

xrange <- c(1,7)
yrange <- c(100,400)

plot(xrange, yrange, type = "n", xlab = "Year", ylab = "Inventory Used", bty = "l")
colors <- rainbow(12)
linetype <- 1

for(i in 1:12){

  currentMonth <- subset(n.ts, cycle(n.ts) == i)
  lines(currentMonth, type = "l", lwd = 1,
       
  col =colors[i]
 
  )
}
title("Item N - Inventory Used \nBroken out by Month ")

legend(6.5,400, 1:12, cex = 0.8, col = colors,lty = linetype, title = "Month", xpd = NA, bty = "n")

par(mfrow = c(1,2))
xrange <- c(1,7)
yrange <- c(0,400)

plot(xrange, yrange, type = "n", xlab = "Year", ylab = "Inventory Used", bty = "l")
colors <- rainbow(12)
linetype <- 1

for(i in 1:12){

  currentMonth <- subset(o.ts, cycle(o.ts) == i)
  lines(currentMonth, type = "l", lwd = 1,
       
  col =colors[i]
 
  )
}
title("Item O - Inventory Used \nBroken out by Month ")

xrange <- c(1,7)
yrange <- c(0,200)

plot(xrange, yrange, type = "n", xlab = "Year", ylab = "Inventory Used", bty = "l")
colors <- rainbow(12)
linetype <- 1

for(i in 1:12){

  currentMonth <- subset(s.ts, cycle(s.ts) == i)
  lines(currentMonth, type = "l", lwd = 1,
       
  col =colors[i]
 
  )
}
title("Item S - Inventory Used \nBroken out by Month ")

legend(6.5,175, 1:12, cex = 0.8, col = colors,lty = linetype, title = "Month", xpd = NA, bty = "n")
```


**Has a similar problem been solved by others? If yes, then please cite those sources.**

Last semester, in Supply Chain with Professor Kohli, my team tackled inventory management. We attempted to build a system using historical data to forecast several months out. With the forecasted values we used the Economic Order Quantity (EOQ) model to calculate safety stock and reorder points. I was taked with the forecasting and EOQ calculations. I am a little embarrassed to tell exactly how I did this, but now, armed with Predictive Analytics, I feel I can revisit the material for find the best forecasting model. 

