---
title: "Tableau"
author: "Christine Iyer"
date: "August 16, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(knitr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(scales)
library(lubridate)
```





Here is the scenario:

Given the start dates of the FSRs in yellow in the FSR (Field Service Reps) Team start date file, how long did it take for them to mature to the point where their average visits per week matched that of their peers?

Please create a Tableau visualization that answers this question as well as visualizations for anything else interesting you see in the data set.

Let me know if you would be willing to do this and a ball park for when you think you will be ready to present to the team and I will get something scheduled. Also please feel free to reach out with any questions.

Thank you!



```{r}
fullData <- read.csv("FullData.csv", header = T)
startDates <- read.csv("startDates.csv", header = T)
Combined <- read.csv("vLoolUp.csv", header = T, stringsAsFactors = F)
```

###This is the actual data

Full Data

```{r}
head(fullData)
tail(fullData)
dim(fullData)

```

```{r}
#make a copy of the data
fullDataNew <- fullData
```

```{r}
#convert factor dates to Posixct
fullData$Actual.Activity.Date <- as.POSIXct(fullData$Actual.Activity.Date, format = "%m/%d/%Y")
fullData$Week.Ending <- as.POSIXct(fullData$Week.Ending, format = "%m/%d/%Y")
fullData$Activity.Recorded.On <- as.POSIXct(fullData$Activity.Recorded.On, format = "%m/%d/%Y")
#make sure the conversion worked

```

```{r}

Combined$Actual.Activity.Date <- as.POSIXct(Combined$Actual.Activity.Date, format = "%m/%d/%Y")
Combined$Week.Ending <- as.POSIXct(Combined$Week.Ending, format = "%m/%d/%Y")
Combined$Activity.Recorded.On <- as.POSIXct(Combined$Activity.Recorded.On, format = "%m/%d/%Y")
Combined$HireDate <- as.POSIXct(Combined$HireDate, format = "%m/%d/%Y")

```


```{r}
workersPerStatus <- Combined %>% group_by(FSR, Status) %>% summarise(n=n())

Averages <- Combined %>% group_by(WNumber, Status) %>% summarise(visitsPerWeek = mean(n()))


```

This is a new dataset reengineering the FSR names

```{r}
#Split FSR names so they match with the other dataset. This is a new dataframe
fullData <- fullData %>% 
  separate(Activity.Recorded.By, c("LastName", "FirstName"), ",")
fullData <- fullData %>% mutate(FSR = paste(LastName, ", ", FirstName)) %>% arrange(desc(Actual.Activity.Date))

#turns out there are many missing values in dates 

fullData[c(19900:19920), ]
```

This puts the days of the week in

```{r}
a <- fullData %>% arrange(Actual.Activity.Date)


# a <- a %>% mutate(Day = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", 
#     "Friday", "Saturday")[as.POSIXlt(a$Actual.Activity.Date)$wday + 1])
# a <- a %>% mutate(DayWeekEnding = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", 
#     "Friday", "Saturday")[as.POSIXlt(a$Week.Ending)$wday + 1])
# 
# head(a)
# tail(a, 100)
```

This numbers the days of the week

```{r}
c <- a %>% mutate(Day = ifelse(wday(a$Actual.Activity.Date)==1,6,wday(a$Actual.Activity.Date)-2)) 
c <-  c %>% mutate(DayWkEnd = ifelse(wday(a$Week.Ending)==1,6,wday(a$Week.Ending)-2))


c %>% group_by(Day) %>% summarise(n = n())
c %>% group_by(DayWkEnd) %>% summarise(n = n())

```


```{r}
#add week number as a new column
e <- a %>% mutate(WeekNumber = format(Actual.Activity.Date, format = "%W"))
e$WeekNumber <- as.numeric(e$WeekNumber)

#Split 2015 and 2016
#2015
e1 <- e[c(1:32967), ]
#add week number to 2015 (this is a duplicate column so it will match with 2016)
e1 <- e1 %>% mutate(WNumber = WeekNumber + 0)
#2016
e2 <- e[c(32968:46755), ]
#add week number (+52) to 2016
e2 <- e2 %>% mutate(WNumber = WeekNumber + 52)
#Recombine 2015 and 2016 so there's a continuous flow of week numbers
perfectFullSet <- rbind.data.frame(e1, e2)
#verify the dimensions are the same as the original data
dim(perfectFullSet)
#eliminate duplicate column
perfectFullSet <- perfectFullSet[, -21 ]


perfectFullSet1 <-  perfectFullSet %>% group_by(WNumber) %>% summarise(n = n())

ggplot(perfectFullSet1, aes(x = WNumber , y = n)) + geom_line()



```



#Week Number




#This has the days of the actual and the week ending Day

```{r, eval=FALSE, include=FALSE}
d <- c %>% mutate(ActualDay = ifelse(Day == 0, "Monday", ifelse(Day == 1, "Tuesday", ifelse(Day == 2, "Wednesday", ifelse(Day == 3, "Thursday", ifelse(Day == 4, "Friday", ifelse(Day == 5, "Saturday", "Sunday")))))))
d <- d %>% mutate(ActualDayWkEnd = ifelse(DayWkEnd == 0, "Monday", ifelse(DayWkEnd == 1, "Tuesday", ifelse(DayWkEnd == 2, "Wednesday", ifelse(DayWkEnd == 3, "Thursday", ifelse(DayWkEnd == 4, "Friday", ifelse(DayWkEnd == 5, "Saturday", "Sunday")))))))

```



#have to make the DayWkEnd total to 6

```{r, eval=FALSE, include=FALSE}

#Weeks end on Sundays and these are all the mising values
b <- a %>% group_by(DayWeekEnding) %>% summarise(n = n()) 

a[c(32900:32999), ]
b[c(32900:32999), ]
```




Start Dates

```{r}
head(startDates)
# x <- levels(fullData$Activity.Recorded.By)
# y <- levels(startDates$FSR)


```

Full Data Split the names

```{r, eval=FALSE, include=FALSE}
head(fullData)
fullData1 <- fullData %>% 
  separate(Activity.Recorded.By, c("LastName", "FirstName"), ",")
fullData1 <- fullData1 %>% mutate(FSR = paste(LastName, ", ", FirstName))
fullData1$Actual.Activity.Date <- as.POSIXct(fullData1$Actual.Activity.Date, format = "%m/%d/%Y")
fullData1$Week.Ending <- as.POSIXct(fullData1$Week.Ending, format = "%m/%d/%Y")
fullData1$Activity.Recorded.On <- as.POSIXct(fullData1$Activity.Recorded.On, format = "%m/%d/%Y")

c <- fullData1 %>% group_by(FSR, Actual.Activity.Date)

#concerned with RepRole
```

Start Dates
Redone so last name first

```{r, echo=TRUE}
startDates1 <- startDates %>% separate(FSR, c("FirstName", "MI", "LastName"), " ") 
startDates1
startDates1[13,3] <- "Lewis"
startDates1[14,3] <- "George"
startDates1[15,3] <- "Deverell"
startDates1[30,3] <- "Chapman"
startDates1[31,3] <- "Orr"
startDates1[32,3] <- "Ziegler"
startDates1[35,3] <- "Miller"  
startDates1[41,3] <-  "Chevalier" 
startDates1[42,3] <- "Garcia"   
startDates1[43,3] <- "Boggs"
startDates1[44,3] <- "Deslauriers"
startDates1[53,3] <-  "Mosher"
startDates1[60,3] <-  "Delaney" 
startDates1[76,3] <-  "Berndt"
startDates1[86,3] <-  "Mumbower"
startDates1[88,3] <-  "Norwood"
startDates1[91,3] <- "Rios"
startDates1[93,3] <-  "Chavoustie"
startDates1[94,3] <-  "Schmit" 
startDates1
#startDates1$colNumber <- seq(1, 94, by = 1)
startDatesFinal <- startDates1 %>% mutate(FSR = paste(LastName,", ", FirstName)) %>% select(FSR, Manager, Last.Hire.Date)
startDatesFinal$Last.Hire.Date <- as.POSIXct(startDatesFinal$Last.Hire.Date, format = "%m/%d/%Y")

```



```{r, eval=FALSE, include=FALSE}
lastNames <- c("Morocutti", "Woolum", "Morocutti", "Morocutti", "Morocutti", "Morocutti", "Woolum","Woolum","Woolum","Woolum","Morocutti", "Woolum","Morocutti", "Woolum")
startDates1[c(15, 31, 32, 35, 41, 60, 76), 4] <- "Morocutti"
startDates1[c(19, 53, 56, 57, 58, 73, 79,94), 4] <-  "Woolum"
startDates1 <- startDates1%>% arrange(LastName)

```


New Hires

```{r}

yellowHires <- startDatesFinal[c(52:70), ]
yellowHires$Status <- rep("Yellow Hire")

```


```{r}

oldHires <- startDatesFinal[c(1:51), ]
oldHires$Status <- rep("Old Hire")

```
```{r}
latestHires <- startDatesFinal[c(71:94),]
latestHires$Status <- rep("Latest Hires")

```


```{r}
perfectStartDates <- rbind(oldHires, yellowHires, latestHires)
perfectStartDates[c(52:53), 3] <- as.POSIXct("2014-10-13")


```


```{r}
# write.csv(fullData1, "fullSet.csv", row.names = F)
#write.csv(perfectStartDates, "perfectStartDates.csv", row.names = F)
#write.csv(perfectFullSet, "perfectFullSet.csv", row.names = F)
```


fullData1 Subsetting

```{r}
fullDataNew <- fullDataNew %>% 
  separate(Activity.Recorded.By, c("LastName", "FirstName"), ",")
fullDataNew <- fullDataNew %>% mutate(FSR = paste(LastName, ", ", FirstName))
head(fullDataNew)


list2env(split(fullDataNew, fullDataNew$FSR), envir = .GlobalEnv)
`Pettinella ,   Stephanie`
`Munsen ,   Karen`
`Munsen ,   Karen` %>% group_by(Actual.Activity.Date) %>% summarise(n = n())
`Munsen ,   Karen`$Actual.Activity.Date <- as.Date(`Munsen ,   Karen`$Actual.Activity.Date, format = "%m/%d/%Y")

```
```{r}
cleanStartDates <- perfectStartDates %>% arrange(Last.Hire.Date)

x <- ggplot(cleanStartDates, aes(x = FSR, y = factor(Last.Hire.Date), fill = Status))+ geom_bar(stat = "identity") + theme(axis.text.y = element_text(angle = 90, hjust = 1)) + theme_bw() + theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

```{r, fig.height=7, fig.width=9}
dataHires <- read.csv("vLoolUp.csv", header = T)
dataHires$HireDate <- as.Date(dataHires$HireDate, format = "%m/%d/%Y")

dataHiresGroups <- dataHires %>% group_by(FSR, HireDate, Status ) %>% summarise(n = n()) %>% mutate(Status1 = ifelse(Status == "Yellow Hire","Interest", "Everyone Else")) %>% arrange(HireDate)

ggplot(dataHiresGroups, aes(x = FSR, y = n, color = Status1, fill = Status1)) + geom_bar(stat = "identity")+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r, fig.height=8, fig.width=9}
ggplot(dataHiresGroups, aes(x = HireDate, y = FSR, color = Status1, fill = Status1, size = n)) + geom_point() + theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
```
```{r, eval=FALSE, fig.height=10, fig.width=10, include=FALSE}
groupsByWeek <- dataHires %>% group_by(WNumber, FSR) %>% summarise(n = n())

#ggplot(groupsByWeek, aes(x = WNumber, y = n, colour=FSR, group=FSR))+ geom_line(stat = "identity") + theme(legend.position="none")
```

```{r}
yellows <- dataHires %>% filter(Status == "Yellow Hire") %>% group_by(WNumber, FSR, Status) %>% summarise(n = n())

#mean visits per week by yellows
yellows %>% group_by(WNumber) %>% summarise(mean(n))
#ggplot(yellows, aes(WNumber, n, color = FSR, group = FSR))+ geom_line()
```


```{r}
list2env(split(dataHires, dataHires$FSR), envir = .GlobalEnv)
#`Willis ,   Jennifer`
```




```{r}
#FSR, WeekNumber, Hire Date, Status
dataHires1 <- dataHires[, c(20:23)] 


```

```{r}
#dataHires1 %>% group_by(FSR, Status, WNumber) %>% summarise(numberVisitsWeek = n())
 #ggplot(dataHires1, aes(x = WNumber, y = sum(numberVisitsWeek)/count(numberVisitsWeek), group = Status )) + geom_line()
```

Group by Week

```{r, fig.height=25, fig.width=10}
aaaa <- dataHires1 %>% group_by(WNumber, FSR, Status) %>% summarise(numberVisitsPerWeek = n())

aaaa %>% group_by(WNumber, Status) %>% summarise(n = n())

ggplot(aaaa, aes(x = WNumber, y = numberVisitsPerWeek, group = FSR, color = Status)) + geom_line() + facet_wrap(~FSR, ncol = 4)
aaaa1 <- aaaa %>% filter(Status == "Yellow Hire")

aaaa2 <- aaaa %>% filter(Status == "Old Hire")
both <- rbind.data.frame(aaaa1, aaaa2)

colors <- c("blue", "gold")

```


Number of Records Per FSR


```{r}
cccc <- dataHires1 %>% group_by(FSR, Status) %>% summarise(totalVisitsPerWorker = n())
dim(cccc)
head(cccc)
```

Number of FSR per Status

```{r}
#number in each status
bbbb <- cccc %>% group_by(Status) %>% summarise(workersNum = n())
bbbb
```


```{r}
eeee <- inner_join(aaaa, bbbb)
head(eeee)
dim(eeee)
```
```{r}
ffff <- eeee %>% group_by(WNumber, Status) %>% summarise(n = n())
dim(ffff)
head(ffff)
tail(ffff)
```




Old Hires Mean

```{r}
OldHiresMean <- dataHires1 %>% filter(Status == "Old Hire") %>% group_by(WNumber, FSR, Status)%>% summarise(n = n())
OldHiresMean
```


```{r}

meanNotYellow <- dataHires1 %>% filter(Status != "Yellow Hire")  %>% group_by(WNumber, FSR, Status) %>% summarise(n = n()) %>% mutate(Status = "Yellow Hire")
head(meanNotYellow)
tail(meanNotYellow)
dim(meanNotYellow)
meanNotYellow
```

```{r}
yellowHiresNamed <- dataHires1 %>% filter(Status == "Yellow Hire") %>% group_by(FSR, WNumber) %>% summarise(n = n()) %>% mutate(Status = "Yellow Hire")
```



```{r}
meanYellow <- dataHires1 %>% filter(Status == "Yellow Hire")  %>% group_by(WNumber) %>% summarise(AveragePerWrkPerWeek = round(n()/19, 2)) %>% mutate(Status = "Yellow Hire", FSR = "Yellow Hire Average") %>% select(WNumber, FSR, Status, n = AveragePerWrkPerWeek)

meanYellow
```


Old Hired Worker Average per Week

```{r}
OldHiresMean <- dataHires1 %>% filter(Status == "Old Hire")  %>% group_by(WNumber) %>% summarise(AveragePerWrkPerWeek = round(n()/52, 2)) %>% mutate(Status = "Old Hire", FSR = "Old Hire FSR Average") %>% select(WNumber, FSR, Status, n = AveragePerWrkPerWeek)
head(OldHiresMean)
tail(OldHiresMean)
dim(OldHiresMean)
OldHiresMean
head(meanNotYellow)
```

Latest = 9

```{r}
LatestHiresMean <- dataHires1 %>% filter(Status == "Latest Hires")  %>% group_by(WNumber) %>% summarise(AveragePerWrkPerWeek = round(n()/9, 2)) %>% mutate(Status = "Latest Hires", FSR = "Latest Hire FSR Average")%>% select(WNumber, FSR, Status, n = AveragePerWrkPerWeek)
head(LatestHiresMean)
tail(LatestHiresMean)

LatestHiresMean
```

Unknowns = 26

```{r}
UnknownMean <- dataHires1 %>% filter(Status == "Unknown Hire Date")  %>% group_by(WNumber) %>% summarise(AveragePerWrkPerWeek = round(n()/26, 2)) %>% mutate(Status =  "Unknown Hire Date", FSR = "Unkn Hire Date FSR Average")%>% select(WNumber, FSR, Status, n = AveragePerWrkPerWeek)


```


```{r, eval=FALSE, fig.height=25, fig.width=9, include=FALSE}
ggplot() + 
  geom_line(aes(WNumber, n, alpha = 1), OldHiresMean) +  
  geom_line(aes(WNumber, n, colour=FSR, alpha=0.4), meanNotYellow)+theme_bw() + theme(legend.position="none") 
```


```{r}
theSet <- rbind.data.frame(meanNotYellow, OldHiresMean, LatestHiresMean, UnknownMean)
theSet
```


```{r, fig.height=6, fig.width=8}
head(OldHiresMean)
head(yellowHiresNamed)
ggplot(OldHiresMean, aes(x = WNumber, y = n)) + 
  geom_line(colour="blue", size = 1.3, linetype = "dashed") + 
  #geom_line(data=LatestHiresMean,aes(WNumber, n), size = 1.4, color = "grey") +       
  #geom_line(data=UnknownMean,aes(WNumber, n), size = 1.4, color = "blue") + 
  geom_line(data=meanYellow,aes(WNumber, n), size = 1.4, color = "yellow", size = 1.3) +theme_bw()
```


```{r, fig.height=20, fig.width=10}
tail(OldHiresMean)
yellowHiresNamed <- yellowHiresNamed %>% select(WNumber, FSR, Status, n)
head(yellowHiresNamed)
yellowHiresNamed1 <- rbind.data.frame(yellowHiresNamed, OldHiresMean)
ggplot(yellowHiresNamed, aes(x = WNumber, y = n, group = FSR, color = Status)) + 
  geom_line(color = "yellow") +
  
  
  facet_wrap(~ FSR, ncol = 4) + 
  geom_line(data = yellowHiresNamed1, aes(x = WNumber, y = n))  +
  theme_bw()

smallOldHires <- OldHiresMean %>% select(WNumber, AvNum = n)
head(smallOldHires)
newerYe <- inner_join(yellowHiresNamed, smallOldHires)
head(newerYe)
```

```{r, fig.height=20, fig.width=9}
ggplot(newerYe, aes(x = WNumber, y = n)) + geom_line(aes(y = AvNum, colour = AvNum)) + geom_line(aes(y = n, color = n)) + facet_wrap(~FSR, ncol = 4) +theme_bw()
```



```{r}
head(yellowHiresNamed)
ggplot(OldHiresMean, aes(WNumber, n)) + geom_line(color = "blue") + geom_line(data = yellowHiresNamed, aes(WNumber, n, color = "yellow")) + facet_wrap(~ FSR)
```


```{r}
meanNotYellow <- meanNotYellow %>% group_by(WNumber, Status) %>% summarise(meanWeeklyActivity = mean(n)) 
head(meanNotYellow)
dim(meanNotYellow)
tail(meanNotYellow)
```
Subsets 

```{r}
head(yellows)
list2env(split(yellows, yellows$FSR), envir = .GlobalEnv)
`Willis , Jennifer`
ggplot(`Willis , Jennifer`, aes(WNumber, n)) + geom_line() +ggtitle(label = "Jennifer Willis")
ggplot(`Martin , Kristen`, aes(WNumber, n)) + geom_line() +ggtitle(label = "Kristen Martin")
head(`Willis ,   Jennifer`)
```

```{r}
tol21rainbow= c("#771155", "#AA4488", "#CC99BB" )
                
                # , "#114477", "#4477AA", "#77AADD", "#117777", "#44AAAA", "#77CCCC", "#117744", "#44AA77", "#88CCAA", "#777711", "#AAAA44", "#DDDD77", "#774411", "#AA7744", "#DDAA77", "#771122", "#AA4455", "#DD7788"
                
               
head(meanNotYellow)

`Pettinella , Stephanie`
ggplot(meanNotYellow, aes(WNumber, meanWeeklyActivity, group = Status, color = Status)) + geom_line(size = 1) + geom_line(data=`Pettinella , Stephanie` ,aes(WNumber, n, color="Pettinella ,   Stephanie"), size = 1.4) + scale_color_manual(values=c("darkmagenta", "darkblue","darkslategray4", "blue")) + theme_bw() 
#+ scale_color_hue(l=60, c=45) 
    
```


```{r}
ggplot(meanNotYellow, aes(WNumber, meanWeeklyActivity, group = Status, color = Status)) + geom_line(size = 1) + geom_line(data= `Luce , Heidi`,aes(WNumber, n, color="Heidi Luce"), size = 1.4) + scale_color_manual(values=c("darkmagenta", "darkblue","darkslategray4")) + theme_bw() + scale_color_hue(l=60, c=45) 
```

```{r}
ggplot(meanNotYellow, aes(WNumber, meanWeeklyActivity, group = Status, color = Status)) + geom_line(size = 1) + geom_line(data=`Willis , Jennifer`,aes(WNumber, n, color="Jennifer Willis"), size = 1.4) + scale_color_manual(values=c("darkmagenta", "darkblue","darkslategray4")) + theme_bw() + scale_color_hue(l=60, c=45) 
```

```{r}
str(dataHires$DPC.Territory)
dataHires$DPC.Territory <- as.character(dataHires$DPC.Territory)
str(dataHires$Practice.Name)
str(dataHires$Sales.Region)
levels(dataHires$Sales.Region)
levels(dataHires$DPC.Territory)
```


```{r, eval=FALSE, include=FALSE}

library(ggmap)
library(leaflet)
coordinatesDPC <- dataHires %>% group_by(DPC.Territory) %>% summarise(n = n())
head(coordinatesDPC)
#Coord <- geocode(coordinatesDPC$DPC.Territory)
tail(Coord)
Coord <- cbind.data.frame(coordinatesDPC, Coord)
#write.csv(Coord, "DPCTerritories.csv", row.names = F)
```

