---
title: "R Notebook"
output: html_notebook
---

Load the Data and Clean it up

"C:\Users\Chris Iyer\Downloads\949497.csv"
"C:\Users\Chris Iyer\Downloads\949053.csv"
```{r}
setwd("C:/Users/Chris Iyer/Documents/R/myrepo/")
library(dplyr)
library(lubridate)
library(knitr)
library(forecast)
library(caret)
rain <- read.csv("949053.csv", header = TRUE)
rain <- rain[-c(1, 4:5, 9:17)]
rain <- rain[10772:11969,]
rainPortland <- rain %>% mutate(STATION_NAME = gsub(" INTERNATIONAL JETPORT ME US", "", STATION_NAME))

head(rainPortland)
#replace -9999 with NA values
rainPortland[rainPortland == -9999] <- NA
rainPortland[ , 2 ] <- ymd(rainPortland[, 2])
rainPortland <- rainPortland %>% select(STATION_NAME,Date = DATE, InchesRain = PRCP, SnowDepth = SNWD, Snow = SNOW)
rainPortland <- rainPortland %>%  mutate(WasThereRain = ifelse(InchesRain > 0, 1,0))

```

Plot to look for anything interesting

```{r}
rain.ts <- ts(rainPortland$InchesRain, start = 2014, frequency = 360)

canadaQuad1 <- tslm(rain.ts ~ trend + I(trend^2) + I(trend^3))
plot(rain.ts)
lines(canadaQuad1$fitted.values, col = "red")
rainMonthly <- aggregate.ts(rain.ts, nfrequency = 12, FUN = sum)
plot(rainMonthly)

seasonPlot <- ggseasonplot(rainMonthly)
seasonPlot

```

Add Lag, Sin, and Cos

```{r}
rainVersion1 <- rainPortland %>% mutate(RainLag = lag(InchesRain, value = 1))
rainVersion2 <- rainVersion1 %>% mutate(RainLag1 = lag(WasThereRain, value = 1))
head(rainVersion2)
rainVersion2$time <- seq.int(1:1198)
tail(rainVersion2)

```

Add seasonal sin and cosine

```{r}
rainVersion2 <- rainVersion2 %>% mutate(seasonalSine = sin(2*pi*rainVersion2$time/365.25), seasonalCosine = cos(2*pi*rainVersion2$time/365.25))
head(rainVersion2)


```


Naive Model Forecast and Confusion Matrix

```{r}
naiveTrain <- rainVersion2$WasThereRain[(length(rainVersion2$WasThereRain) - 1 - 467) : (length(rainVersion2$WasThereRain)- 1)]
naiveTrain[1:10]
confusionMatrix(naiveTrain, rainVersion2$WasThereRain[(length(rainVersion2$WasThereRain) - 467) : length(rainVersion2$WasThereRain)], positive = c("1"))
```



Log Reg Model

```{r}
trainOut <- rainVersion2[1:730, ]
outLogReg <- glm(WasThereRain ~ RainLag1 + seasonalSine + seasonalCosine, family = "binomial", data = trainOut)
summary(outLogReg)
predictions <- predict(outLogReg, rainVersion2[731:1198, ], type = "response")
```




Forecast 

```{r}
predictions1 <- (ifelse(predictions > 0.5, 1,0))
predictions[190]
```

Accuracy

```{r}
confusionMatrix(ifelse(predictions > 0.44, 1,0), rainPortland[731:1198, ]$WasThereRain, positive = c("1"))
```


```{r}
predictions <- as.data.frame(predictions)
validDate <- as.Date("2016-01-01")
validDate <- validDate + 0:467
forecast <- cbind(validDate, predictions)
validationPeriod <- rainPortland[731:1198,]
validationPeriod1 <- cbind(validationPeriod,forecast)
validationPeriod1 <- validationPeriod1 %>% mutate(willThereBeRain = ifelse(predictions > 0.5, "Yes", "No"))
validationPeriod1 <- validationPeriod1 %>% mutate(willThereBeRain1 = ifelse(predictions > 0.5, 1, 0))
validationPeriod1 <- validationPeriod1 %>% mutate(WasTheForecastRight = ifelse(WasThereRain == willThereBeRain1, "Yes, Correct", "Not Quite"))
summer2016 <- validationPeriod1[122:305,]
summer2016 %>% filter(WasTheForecastRight == "Not Quite") %>% select(Date, WasTheForecastRight, WasThereRain, willThereBeRain1, InchesRain)
```



```{r}

```


```{r}
logRegression <- glm(WasThereRain ~ RainLag1 + seasonalSine + seasonalCosine, family = "binomial", data = rainVersion2)
summary(logRegression)
predictions <- predict(logRegression, 21, type = "response")
```



**Last summer, the forecast was wrong 32% of the time.**

**Let's break it down by month**

**May**

got it wrong 39%

```{r}
May <- summer2016[1:31,]
May %>%  filter(WasThereRain == 1) %>% mutate(Prediction = ifelse(willThereBeRain1 == 1, "Predicted Rain Correctly", "Predicted Sun, But it Rained")) %>% select(Date, WasTheForecastRight, Prediction )

```

```{r}
May %>% filter(WasThereRain == 0) %>% mutate(Prediction = ifelse(willThereBeRain1 == 0, "Predicted Sun Correctly", "Predicted Sun, but it rained"))%>% select(Date, WasTheForecastRight, Prediction )
```


```{r}
May %>% filter(WasThereRain == 1) %>% mutate(Prediction = ifelse(willThereBeRain1 == 0, "Predicted Sun, but it rained", "Predicted Rain Correctly"))%>% select(Date, WasTheForecastRight, Prediction )
```

```{r}
May %>% filter(WasThereRain == 0) %>% mutate(Prediction = ifelse(willThereBeRain == 1, "Predicted rain, but it was sunny", "Predicted sun correctly") )%>% select(Date, WasTheForecastRight, Prediction )

```

```{r}
May <- summer2016[1:29,] %>% filter(WasTheForecastRight == "Not Quite") %>% select(Date, WasThereRain, willThereBeRain1,  WasTheForecastRight)
May
```

**June**

got it wrong 37% in June

```{r}
June <- summer2016[32:61,]
June
June <- summer2016[32:61,] %>% filter(WasTheForecastRight == "Not Quite") %>% select(Date, WasThereRain, WasTheForecastRight)
```

Got it wrong 29% in July

```{r}
July <- summer2016[62:92,]
July %>% filter(willThereBeRain1 == 1) %>% filter(WasThereRain == 1)
July <- summer2016[62:92,] %>% filter(WasTheForecastRight == "Not Quite") %>% select(Date, WasThereRain, WasTheForecastRight)
July
```


got it wrong 26% in August


```{r}
August <- summer2016[93:123,] 
August
August <- summer2016[93:123,] %>% filter(WasTheForecastRight == "Not Quite") %>% select(Date, WasThereRain, WasTheForecastRight)
August
```

#Got it wrong 23% in September

```{r}
September <- summer2016[124:153,]
September
September <- summer2016[124:153,]

September <- summer2016[124:153,] %>% filter(WasTheForecastRight == "Not Quite") %>% select(Date, WasThereRain, WasTheForecastRight)
September

```

Got it wrong 39% in October

```{r}
October <- summer2016[154:184,]
October
October <- summer2016[154:184,] %>% filter(WasTheForecastRight == "Not Quite") %>% select(Date, WasThereRain, WasTheForecastRight)

October %>% filter(willThereBeRain1 == 1)
```


```{r}
Month <- c("May", "June", "July", "August", "September", "October")

 
NailedItSunny <- summer2016 %>% filter(WasThereRain == 0 && willThereBeRain1 == 0) 
dim(NailedItSunny)
NailedItSunny
NailedItRain <- summer2016 %>% filter(WasThereRain == 1 && willThereBeRain1 == 1)
dim(NailedItRain)
```


**Forecasted Rain**

```{r}
x <- summer2016 %>% filter(WasThereRain == 1 && willThereBeRain1 == 1) %>% select(Date, WasThereRain, willThereBeRain1, WasTheForecastRight)
x
```
**This is the same test with the lag removed**
```{r}
trainOut <- rainVersion2[1:730, ]
outLogReg1 <- glm(WasThereRain ~ seasonalSine + seasonalCosine, family = "binomial", data = trainOut)
summary(outLogReg1)
predictions2 <- predict(outLogReg1, rainVersion2[731:1198, ], type = "response")
head(predictions2)
predictions3 <- (ifelse(predictions2 > 0.5, 1,0))
head(predictions3)
confusionMatrix(ifelse(predictions2 > 0.5, 1,0), rainPortland[731:1198, ]$WasThereRain, positive = c("1"))
```

Spring and Summer months

```{r}
april17 <- rainPortland[1187:1198, ]
april17
april16 <- rainPortland[822:833,]
april16
  april15 <-rainPortland[456:467,] 
  april15
  april14 <- rainPortland[91:102,] 
  april14
  aprils <- rbind(april14,april15,april16, april17)
  aprils
  aprils.ts <- ts(aprils$InchesRain, start = 2014, frequency = 12)
  ggseasonplot(aprils.ts, xaxt = "n", yaxt = "n", xlab = "Year", ylab = "Souvenir Sales (thousands)", main = "Daily Rain")
axis(1, at=seq(1,12,1), labels=format(seq(1,12,1)))
# Add the y-axis
axis(2, at = seq(7, 11, 1), labels = format(round(exp(seq(7, 11, 1)), digits = 0), las = 2))
kable(head(rainPortland))
dim(rainPortland)
```


**Try the melbourne**

```{r}
setwd("/Users/Chris Iyer/Documents/")
melbourseRain <- read.csv("MelbourneRainfall.csv", header = TRUE, stringsAsFactors = FALSE)
rain.ts <- ts(melbourseRain$mmRain, start = c(2000,1), frequency = 360)
melbourseRain <- melbourseRain %>% mutate(rainy = ifelse(Rainfall.amount..millimetres. > 0, 1,0)) %>% rename(mmRain = Rainfall.amount..millimetres.)
head(melbourseRain)
rainMonthly <- aggregate.ts(rain.ts, nfrequency = 12, FUN = sum)
ggseasonplot(rainMonthly, lwd = 2)
plot(rainMonthly)
melbourseRain$time <- seq.int(1:4322)
melbourneRain2 <- melbourseRain %>% mutate(seasonalSine = sin(2*pi*melbourseRain$time/365.25), seasonalCosine = cos(2*pi*melbourseRain$time/365.25))

melbourneRain2 <- melbourneRain2 %>% mutate(RainLag = lag(mmRain, value = 1))
melbourneRain2 <- melbourneRain2 %>% mutate(RainLag1 = lag(rainy, value = 1))
head(melbourneRain2, 15)

dim(melbourseRain)
trainOut <- melbourneRain2[1:3653,]

x <- glm(rainy ~ RainLag1 + seasonalSine + seasonalCosine, family = "binomial", data = trainOut )
summary(x)
predictions <- predict(x, melbourneRain2[3654:4322 ,], type = "response")
#this is for the validation period
confusionMatrix(ifelse(predictions > 0.5,1,0), melbourneRain2[3654:4322, ]$RainLag1, positive = c("1"))
```

